Global adjoint tomography -- Model GLAD-M25\footnote{This paper is dedicated to Dimitri Komatitsch, computational geophysicist extraordinaire, who passed away unexpectedly shortly before its submission.}

### 2019-01-28 main.tex
Updates from ShareLaTeX

\begin{figure}
  \centering
  \includegraphics[width=0.9\textwidth]{figures/window_colorbar_linear_Z.pdf}
  \caption{Time-distance plot for vertical component 17--40~s body waves showing a measurement window density map.
  A total of 4,363,719 time windows were discretized into 1~degree epicentral distance and 1~s time bins. Major traveltime branches are labeled. Note that the plot contains data from events with a wide variety of depths, so the branches are for identification purposes only.
  }
  \label{fig:window_density}
\end{figure}

@@

Fig.~\ref{fig:P_phase_hist} shows histograms of 17--40~s P-wave traveltime anomalies on the vertical and radial components.
Both components exhibit consistent reductions in terms of both mean and variance. 
These arrivals --- almost 900,000 measurements in the 17--40~s and 40--100~s period bands, roughly~$\sim8\%$ of the database --- are of great importance, because they help constrain the compressional wavespeed structure in the model.

\begin{figure}
  \centering
  \includegraphics[width=0.8\textwidth]{figures/dt_histogram_P.pdf}
  \caption{Histograms of traveltime measurements of 17--40~s P arrivals on the vertical and radial for S362ANI combined with CRUST2.0 (M00, Black), GLAD-M15 (M15, Green), and GLAD-M25 (M25, Red). Other settings are the same as in Fig.~\ref{fig:phase_hist}. {\color{red}Wenjie: remove 40--100~s.}}
  \label{fig:P_phase_hist}
\end{figure}

>>>>

\begin{figure}
  \centering
  \includegraphics[width=0.9\textwidth]{figures/window_colorbar_linear_Z.pdf}
  \caption{Time-distance plot for vertical component 17--40~s body waves showing a measurement window density map.
  A total of 4,363,719 time windows were discretized into 1~degree epicentral distance and 1~s time bins. Major traveltime branches are labeled. Note that the plot contains data from events with a wide variety of depths, so the branches are for identification purposes only.
  }
  \label{fig:window_density_Z}
\end{figure}

Fig.~\ref{fig:window_density_R} and Fig.~\ref{fig:window_density_T} shows for Radial and Transverse component in 17--40~s period bands.

\begin{figure}
  \centering
  \includegraphics[width=0.9\textwidth]{figures/window_colorbar_linear_R.pdf}
  \caption{Same as Fig.~\ref{fig:window_density_Z}, except for Radial component 17--40~s body waves.}
  \label{fig:window_density_R}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=0.9\textwidth]{figures/window_colorbar_linear_T.pdf}
  \caption{Same as Fig.~\ref{fig:window_density_Z}, except for Transverse component 17--40~s body waves.}
  \label{fig:window_density_T}
\end{figure}

@@

Fig.~\ref{fig:P_phase_hist} shows histograms of 17--40~s P-wave traveltime anomalies on the vertical and radial components.
Both components exhibit consistent reductions in terms of both mean and variance. 
These arrivals --- almost 530,000 measurements in the 17--40~s period band, roughly~$\sim3\%$ of the database --- are of great importance, because they help constrain the compressional wavespeed structure in the model.

\begin{figure}
  \centering
  \includegraphics[width=0.8\textwidth]{figures/dt_histogram_P.pdf}
  \caption{Histograms of traveltime measurements of 17--40~s P arrivals on the vertical and radial for S362ANI combined with CRUST2.0 (M00, Black), GLAD-M15 (M15, Green), and GLAD-M25 (M25, Red). Other settings are the same as in Fig.~\ref{fig:phase_hist}.}
  \label{fig:P_phase_hist}
\end{figure}
